R Notebook

### 2021-03-10 eda.Rmd
Analysis on state

- Filtered data such that `api_temp = oxymorphone`
- Dropped `country` and `api_temp`
- Removed observations with missing `ppm` (14)
- Dropped unused levels

@@

>>>>

- Filtered data such that `api_temp = oxymorphone`
- Dropped `country` and `api_temp`
- Removed observations with missing `ppm` (14)
- Dropped unused levels
- Dropped observations where `state == 'USA'`

@@

Missing values?

```{r}
sum(is.na(streetrx$state))
```

No - let's check a table then:

```{r}
table(streetrx$state)
```

Ok, we have 52 levels but we *should* have 50. D.C. is on there which is fine. The other incorrect value is a state of "USA". We'll probably have to drop these, or we could take a look at their cities and manually enter the state

```{r}
streetrx %>% filter(state == 'USA')
```

City is missing, region is missing - we don't have any location information on these observations: drop

```{r}
streetrx <- streetrx %>% filter(state != 'USA')
```
